%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.\usepackage{scrextend}
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[runningheads,a4paper]{llncs}

\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{amssymb}
%\setcounter{tocdepth}{3}
\usepackage{graphicx}   % for the adjustwidth environment

%\usepackage{scrextend}
\usepackage{url}    
\urldef{\mailsa}\path|{anna.bernasconi,claudio.menghi,carlo.ghezzi}@polimi.it| 
\urldef{\mailsb}\path|pspoleti@kennesaw.edu| 
\urldef{\mailsc}\path|lenore@cs.uic.edu|   
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

%%%%%%%%%%%%%%%%%%START CUSTOM SECTION%%%%%%%%%%%%%%%

\usepackage{mathtools}
\usepackage{mathpartir}
\usepackage[inline]{enumitem}
\usepackage{cancel}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{todonotes}
 \usepackage{ltl}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{textgreek}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{changebar}
\usepackage{changes}
\usepackage{multirow}
\usepackage{makecell}

\definecolor{mygreen}{rgb}{0.0, 0.5, 0.0}
\definecolor{myred}{rgb}{0.8, 0.0, 0.0}

\newcommand{\validProof}{\ding{51}}
\newcommand{\validCounterexample}{\textcolor{mygreen}{\ding{52}}}
\newcommand{\notvalidProof}{\ding{55}}%
\newcommand{\spuriosCounterexample}{\textcolor{myred}{\ding{56}}}%

\usepackage{todonotes}
\author{Claudio Menghi}
\definechangesauthor[name={Claudio Menghi},color=orange]{CM}
\author{Anna Bernasconi}
\definechangesauthor[name={Anna Bernasconi},color=red]{AB}

\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

\usepackage{tikz, pgf, pgfplots}
\usetikzlibrary{automata,positioning}
\usetikzlibrary{shapes,shapes.geometric}
\usetikzlibrary{backgrounds}

%utils for automata states
\tikzset{state/.style={
        draw, 
        ellipse, 
        minimum height=2em, 
        minimum width=2.8em,  
        thick } }
\tikzset{statep/.style={
    draw, 
    ellipse, 
    minimum height=1em, 
    minimum width=1em,  
    thick } }
\tikzset{emptynode/.style={ draw } }
\tikzset{empty/.style={ } } 

% per testo barrato
\usepackage[normalem]{ulem}
\newcommand{\cla}[1]{{\color{blue} #1}}
\newcommand{\anna}[1]{{\color{red} #1}}
\newcommand{\paola}[1]{{\color{green} #1}}
\newcommand{\carlo}[1]{{\color{yellow} #1}}


\newcommand{\NAME}{THRIVE}


%%%%%%%%%%%%%%%%%%END CUSTOM SECTION%%%%%%%%%%%%%%%


\begin{document}



\mainmatter  % start of an individual contribution

% first the title is needed
\title{From Three-Valued Model Checking\\ to Temporal Proofs}

% a short form should be given in case it is too long for the running head
\titlerunning{From Three-Valued Model Checking to a Temporal Proof}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%


\author{}
%\author{\phantom{Anna Bernasconi\inst{1}}
%\phantom{\and Claudio Menghi\inst{1}}
%\phantom{\and Paola Spoletini\inst{2} \and } ~\\ 
%\phantom{Lenore D. Zuck\inst{3} \and}
%\phantom{Carlo Ghezzi\inst{1}}}
%
\authorrunning{From Three-Valued Model Checking to Temporal Proof}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{}
%\institute{\phantom{DEIB - DEEPSE group - Politecnico di Milano,}~\\
%%via Golgi 42, I-20133, Milano, Italy\\
%\phantom{\mailsa}~\\
%\phantom{\and Kennesaw State University,}~\\
%%, Marietta, USA
%\phantom{\mailsb}~\\
%\phantom{\and University of Illinois at Chicago,}~\\
%\phantom{\mailsc}~\\
%}


%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle


\begin{abstract}
Model checking automatically verifies whether a model of the system under analysis satisfies a property of interest.
It returns \emph{true} if the property is satisfied, \emph{false} and a violating behavior if it is not. 
Three-valued model checking has been proposed to support verification when some portions of the model are unspecified. 
Differently from the classical two-valued case, it also returns a \emph{maybe} value and a possibly violating behavior if the property satisfaction depends on how the unspecified parts are refined.

When no violating or possibly violating behavior is returned, model checking does not usually provide the designer with any details about the reasons \emph{why} the property is satisfied.
This is the purpose of deductive verification.
Deductive verification frameworks produce a formal proof of the property satisfaction, but have only been studied for the two-valued case.
This paper proposes \NAME, a unified approach that enriches three-valued model checking with a deductive verification engine that generates proofs which explain why a \emph{true} or \emph{maybe} result is returned.
\end{abstract}

\section{Introduction}
\input{sections/Introduction.tex}

\section{Motivating Example.} 
\label{sec:motivating}
\input{sections/motivatingExample.tex}

\section{Background}
\label{sec:preliminaries}
This section presents the modeling formalisms, their properties and verification algorithms upon which \NAME\ is based. It first briefly overviews how functional properties are checked over complete models.
Then it discusses how incomplete models are verified.
Finally, it describes how the deductive verification framework exploits the model checking procedure of complete models to generate a proof that explains why a property is satisfied.
An extended version of the paper, that includes all the formal details, can be found at \url{goo.gl/g3tmzG}.


\subsection{Checking complete models.}
%\textbf{Checking complete models.}
\label{sec:mcComplete}
\input{sections/CheckingCompleteModels.tex}

\subsection{Checking incomplete models.}
%\textbf{Checking incomplete models.}
\label{sec:mcIncomplete}
\input{sections/CheckingIncompleteModels.tex}

\subsection{Deductive verification}
%\textbf{Constructing a Temporal Logic Proof.}
\label{sec:theoremProving}
\input{sections/TheoremProving.tex}

\section{\NAME}
\label{sec:contribution}
\input{sections/Contribution.tex}

%\label{sec:example}
%\input{sections/Example.tex}

\section{Preliminary evaluation}
\label{sec:preliminaryEvaluation}
\input{sections/preliminaryEvaluation.tex}

\section{Discussion}
\label{sec:discussion}
\input{sections/discussion.tex}

\section{Related Work}
\label{sec:stateoftheart}
\input{sections/StateOfTheArt.tex}


\section{Conclusions}
\label{sec:conclusions}
\input{sections/Conclusions.tex}

\bibliographystyle{abbrv}
\bibliography{sigproc} 


%\section*{Appendix:}


\end{document}
